\texttt{GLAD-M25} - global adjoint tomography model

### 2018-09-25 gji_extraguide.tex
fix ref issues

\section{Earthquakes}
In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
and added them into our database, making the total number of earthquakes reach 1,040.
The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
is set at 9 secsince we can use point representation and gaussian source time function.
We also constrain the duration of CMT sources to be smaller than 17s. The locations of 1040
earthquakes is shown in fig.\ref{source_correction}a.

@@

Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we defined the change of model and gradient:\\
\begin{equation*}
    \Delta m_i = m_{i+1} - m_i \quad
    \Delta g_i = g_{i+1} - g_i
\end{equation*}

and \\
\begin{equation*}
     \rho_k = \frac{1}{\Delta g^{T} \Delta m}
\end{equation*}

@@

\begin{table}[!htb]
  \centering
  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
  \label{tab:category}
  \begin{tabular}{|c|c|c|c|}
    \hline
     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &    31.1    &       37.1 &       42.2 \\
    40--100s body waves    &    31.3    &       40.2 &       42.0 \\
    40--100s surface waves &    50.1    &       51.1 &       53.8 \\
    90--250s               &    36.2    &       38.8 &       38.6 \\
    \hline
  \end{tabular}\\
  \label{table:categories}
\end{table}

\begin{table}[!htb]
  \centering
  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
  \label{tab:category}
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &         29.2 &       33.7 &       43.4 \\
    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
    90--250s               &         30.9 &       34.8 &       34.9 \\
    \hline
  \end{tabular}\\
  \label{table:misfit_reduction_M00_M25_360}
\end{table}

\begin{table}[!htb]
  \centering
  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
  \label{tab:category}
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &   17.4   &       21.1 &       24.6 \\
    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
    90--250s               &   14.5   &       13.4 &       25.7 \\
    \hline
  \end{tabular}\\
  \label{table:misfit_reduction_M15_M25}
\end{table}

\begin{table}[!htb]
  \centering
  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
  \label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
  \hline
  17--40s                &          11.8 &       14.1 &       21.5 \\
  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
  90--250s               &          10.9 &       14.3 &       24.0 \\
  \hline
  \end{tabular}\\
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging}) models. Green circles denotes the locations of hotspots. For SL2013NA, we showed the 610km instead of 600km due to its own mesh.}
\label{fig:global-vp}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
\label{fig:global-vp}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
\label{fig:global-vp}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
\label{fig:global-vp}
\centering
\end{figure}

@@

\begin{figure}[h]
    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
\end{figure}

\begin{figure}[h]
    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model asssessment stage. Theses events are not used in the structural inversion. (a) Beach balls of earthquakes. Same color conventions as used in the \ref{fig:} (b) and (c) Histograms of moment magnitude and depth.}
\centering
\end{figure}

>>>>

\section{Earthquakes}
In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
and added them into our database, making the total number of earthquakes reach 1,040.
The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
is set at 9 secsince we can use point representation and gaussian source time function.
We also constrain the duration of CMT sources to be smaller than 17s. The locations of 1040
earthquakes is shown in fig.\ref{fig:source_correction}a.

@@

Assuming the model is $m_i$ and gradient is $g_i$ at iteration i, we
defined the change of model and gradient:

\begin{equation*}
    \Delta m_i = m_{i+1} - m_i \quad
    \Delta g_i = g_{i+1} - g_i
\end{equation*}

and
\begin{equation*}
     \rho_k = \frac{1}{\Delta g^{T} \Delta m}
\end{equation*}

@@

\begin{table}[!htb]
  \centering
  %\label{tab:misfit_reduction_M00_M25}
  \begin{tabular}{|c|c|c|c|}
    \hline
     ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &    31.1    &       37.1 &       42.2 \\
    40--100s body waves    &    31.3    &       40.2 &       42.0 \\
    40--100s surface waves &    50.1    &       51.1 &       53.8 \\
    90--250s               &    36.2    &       38.8 &       38.6 \\
    \hline
  \end{tabular}\\
  \caption{Misfit Reduction from M00 to M25 for 1480 earthquakes used in the inversion}
  \label{table:categories}
\end{table}

\begin{table}[!htb]
  \centering
  %\label{tag:misfit_reduction_M00_M25_360}
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &         29.2 &       33.7 &       43.4 \\
    40--100s body waves    &         26.2 &       32.2 &       39.0 \\
    40--100s surface waves &         49.1 &       49.4 &       51.2 \\
    90--250s               &         30.9 &       34.8 &       34.9 \\
    \hline
  \end{tabular}\\
  \caption{Misfit Reduction from M00 to M25 for 360 earthquakes as held-out dataset}
  \label{table:misfit_reduction_M00_M25_360}
\end{table}

\begin{table}[!htb]
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
    \hline
    17--40s                &   17.4   &       21.1 &       24.6 \\
    40--100s body waves    &   16.8   &       21.3 &       21.7 \\
    40--100s surface waves &   28.5   &       28.3 &       28.4 \\
    90--250s               &   14.5   &       13.4 &       25.7 \\
    \hline
  \end{tabular}\\
  \label{table:misfit_reduction_M15_M25}
  \caption{Misfit Reduction from M15 to M25 for 1480 earthquakes used in the inversion}
\end{table}

\begin{table}[!htb]
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical(\%) & Radial(\%) &  Transverse(\%) \\
  \hline
  17--40s                &          11.8 &       14.1 &       21.5 \\
  40--100s body waves    &          14.5 &       12.9 &       16.9 \\
  40--100s surface waves &          29.3 &       28.1 &       23.7 \\
  90--250s               &          10.9 &       14.3 &       24.0 \\
  \hline
  \end{tabular}\\
  \caption{Misfit Reduction from M15 to M25 for 360 earthquakes as held-out dataset}
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of $V_s$ variations of North America at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging}) models. Green circles denotes the locations of hotspots. For SL2013NA, we showed the 610km instead of 600km due to its own mesh.}
\label{fig:america-vs}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{Map views of $V_s$ variations of Europe at various depths for our model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
\label{fig:europe-vs}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
\label{fig:asia-vs}
\centering
\end{figure}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
\label{fig:southamerica-vp}
\centering
\end{figure}

@@

%\begin{figure}[h]
%    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
%\end{figure}

%\begin{figure}[h]
%    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
%\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model asssessment stage. Theses events are not used in the structural inversion. (a) Beach balls of earthquakes. Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
\centering
\end{figure}
